Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
Use variable for FeatureUnion.

    Pipeline([("pca", FeatureUnion([('pca', PCA()),
                                    ('kpca', KernelPCA(kernel="rbf"))])),
              ("feature_selection", SelectKBest(k=100)),
              ("logistic_model", LogisticRegression(penalty="l2"))
    ]).fit(X_train, y_train).predict(X_test)
\end{verbatim}

>>>>

    feat_union = FeatureUnion([('pca', PCA()),
                               ('kpca', KernelPCA(kernel="rbf"))])

    Pipeline([("pca", feat_union,
              ("feature_selection", SelectKBest(k=100)),
              ("logistic_model", LogisticRegression(penalty="l2"))
    ]).fit(X_train, y_train).predict(X_test)
\end{verbatim}
